The Two-Infall Model Across Space and Time for a Milky Way in Equilibrium

### 2025-03-06 src/tex/ms.tex

% user-defined commands
% \newcommand{\yes}{\textcolor{green}{\checkmark}\xspace}
% \newcommand{\meh}{\textcolor{black}{$\sim$}\xspace}
% \newcommand{\no}{\textcolor{red}{$\times$}\xspace}
\newcommand{\osuaffil}{Department of Astronomy, The Ohio State University, 140 W. 18th Ave, Columbus OH 43210, USA}
\newcommand{\ccappaffil}{Center for Cosmology and AstroParticle Physics, The Ohio State University, 191 W. Woodruff Ave., Columbus OH 43210, USA}
\newcommand{\aFe}{[$\alpha$/Fe]\xspace}
\newcommand{\vice}{{\tt VICE}\xspace}
% \newcommand{\hydro}{{\tt h277}\xspace}
\newcommand{\todo}[1]{{\color{red}#1}}

@@

% Title
\title{A Two-Infall Star Formation History with Outflows and Radial Migration}

% Author list
\author[0000-0003-3781-0747]{Liam O.\ Dubay}
\affiliation{\osuaffil}
\affiliation{\ccappaffil}
\author[0000-0001-7258-1834]{Jennifer A.\ Johnson}
\affiliation{\osuaffil}
\affiliation{\ccappaffil}
\author[0000-0002-6534-8783]{James W.\ Johnson}
\affiliation{Observatories of the Carnegie Institution for Science, 813 Santa Barbara St., Pasadena CA 91101, USA}
% \affiliation{\osuaffil}
% \affiliation{\ccappaffil}
\author[0000-0002-2854-5796]{John D.\ Roberts}
\affiliation{\osuaffil}
\affiliation{\ccappaffil}
% \author[0000-0001-7775-7261]{David H. Weinberg}
\author{coauthors}

@@

\begin{abstract}
    The two-infall model has long been proposed to explain the formation of the Milky Way's thick and thin disks through two consecutive gas accretion episodes. It has successfully reproduced observed abundance patterns such as the [$\alpha$/Fe]-bimodality in the Solar neighborhood and across the disk. However, few studies have explored a two-infall model with significant mass-loaded outflows, nor compared model results with comprehensive age--abundance data across the disk. We run multi-zone galactic chemical evolution (GCE) models with a two-infall star formation history, radially-dependent mass-loaded outflows, and a prescription for radial migration of stellar populations. We compare our model results to abundance patterns across the disk from the Apache Point Observatory Galactic Evolution Experiment (APOGEE) data release 17, supplemented with stellar age estimates using multiple methods. We find that the two-infall model struggles to reproduce all the observed characteristics of the chemical thin disk. Models with low nucleosynthetic yields and outflows experience long-lasting dilution of the gas-phase metallicity which contradicts the local age--metallicity relation. Conversely, models with higher yields and outflows fail to reproduce stellar [$\alpha$/Fe] distributions across the disk \todo{(should I be more specific?)}. These issues can be mitigated, but not completely solved, by enriching the accreted gas to low metallicity. 
\end{abstract}

@@

\todo{Hook, summary of alpha-bimodality.}

% Summary of two-infall literature
The two-infall model was first developed by \citet{chiappini_chemical_1997} to explain the origin of the thick and thin disks. Though the model has been revised and refined since, the basic premise remains the same: the rate of gas infall onto the Galaxy is described by two consecutive, exponentially declining bursts. The relatively low infall rate between the two bursts leads to a hiatus in the star formation rate, and the delayed production of Fe by SNe Ia allows the gas abundance to evolve between the high- and low-$\alpha$ sequences without producing many stars in between. Varying the timescale of the second infall produced inside-out disk growth and a radial abundance gradient. Additionally, the two-infall model of \citet{chiappini_chemical_1997} successfully reproduced Solar neighborhood abundance distributions and the age--metallicity relation.

Subsequent studies refined the two-infall model to reproduce abundance data across the disk \citep[e.g.,][]{chiappini_abundance_2001,chiappini_oxygen_2003}, and others have explored in its context the SN Ia delay-time distribution \citep{matteucci_effect_2009,palicio_analytic_2023}, modifications to the recycling treatment such as galactic fountains and a metal cooling timescale \citep{spitoni_effects_2009}, radial gas flows \citep{spitoni_effects_2011,palla_chemical_2020}, a variable star formation efficiency \citep{spitoni_effects_2011,palla_chemical_2020}, radial stellar migration \citep{spitoni_effect_2015,palla_mgfe_2022}, azimuthal abundance variations due to spiral modes \citep{spitoni_2d_2019}, and pre-enriched gas infall \citep{palla_chemical_2020,spitoni_remind_2024}. Recently, \citet{spitoni_beyond_2023} and \citet{palla_mapping_2024} proposed a third gas accretion event in the last $\sim3$ Gyr to match the inferred star formation history from {\it Gaia} \citep{ruiz-lara_recurrent_2020} and explain the recent abundance evolution of the Solar neighborhood.

\todo{Observational evidence.} \citet{nissen_high-precision_2020} measured abundances and estimated ages for nearby Solar-type stars and reported two sequences in the age--metallicity distribution which could be explained by the two-infall model.

\todo{Outflows. Their arguments against. Our arguments for.}

@@

\begin{table*}
    \centering
    \caption{Median and dispersion in APOGEE parameter uncertainties.}
    \label{tab:uncertainties}
    \begin{tabular}{lcc}
        \hline\hline
        \multicolumn{1}{c}{Parameter} & \multicolumn{1}{c}{Median Uncertainty} & \multicolumn{1}{c}{Uncertainty Dispersion ($95\%-5\%$)} \\
        \hline
        [Fe/H]          & $0.0089$   & $0.0060$ \\
        ${\rm [O/Fe]}$  & $0.019$    & $0.031$ \\
        $\log_{10}(\tau_{\rm latent}/{\rm Gyr})$    & 0.10   & $0.16$ \\
        $\tau_{\rm [C/N]}/{\rm Gyr}$     & 1.0   & \todo{N/A} \\
        \hline
    \end{tabular}
\end{table*}

@@

Our second age catalog uses the [C/N]--age relation for red giant branch and red clump stars. 
\todo{Paragraph describing [C/N]-derived ages (get help from Jack).}
This method has the benefit of providing age estimates for luminous giants, which increases the sample size at farther distances from the Sun. However, systematic effects of the [C/N]--age relation mean that these ages are most trustworthy in the range $1\sim10$ Gyr. We estimate ages for \num{113464} stars across the disk, including \num{20995} in the Solar neighborhood.
\todo{Note about metallicity cutoff for luminous giants.}

@@

\begin{deluxetable*}{Cccl}
    \tablecaption{A summary of variables and their fiducial values for our chemical evolution models (see discussion in Section \ref{sec:methods}).\label{tab:multizone-parameters}}
    \tablehead{
        \colhead{Quantity} & \colhead{Fiducial Value(s)} & \colhead{Section} & \colhead{Description}
    }
    \startdata
        % Yields
        y/Z_\odot       & 1         & \ref{sec:yields}  & Nucleosynthetic yield scaling (see Table \ref{tab:yields}) \\
        N_{\rm Ia}/M_\star  & $1.55\times10^{-3}$       & \ref{sec:yields}  & Integrated Type Ia supernova rate (see Table \ref{tab:yields}) \\
        f_{\rm Ia}(t)   & Plateau   & \ref{sec:yields}  & Delay-time distribution of Type Ia supernovae \\
        % t_D             & 40 Myr    & \ref{sec:yields}  & Minimum SN Ia delay time \\
        % Star formation histories
        % Outflows
        \eta_\odot      & 0.2       & \ref{sec:outflows}    & Outflow mass-loading factor in the Solar annulus ($\eta\equiv \dot\Sigma_{\rm out}/\dot\Sigma_\star$) \\
        R_\eta          & 4.2 kpc   & \ref{sec:outflows}    & Exponential outflow scale radius \\
        f_{\Sigma,0}    & 0.27      & \ref{sec:sfh}     & Central thick/thin disk surface density ratio \\
        {\rm [X/H]}_{\rm CGM}   & Pristine  & \ref{sec:sfh}     & Metallicity of infalling gas \\
        \tau_1          & 1 Gyr     & \ref{sec:parameter-selection}     & Timescale of the first infall epoch \\
        \tau_2(R_\odot)  & 15 Gyr    & \ref{sec:parameter-selection}     & Timescale of the second infall epoch at the Solar annulus \\
        R_{\tau_2}   & 7 kpc     & \ref{sec:parameter-selection}      & Exponential scale radius of the second infall timescale \\
        t_{\rm max}      & 4.2 Gyr  & \ref{sec:parameter-selection}     & Time of maximum gas infall (onset of second infall) \\
        \sigma_{\rm RM8}    & 2.68 kpc  & \ref{sec:migration}   & Radial migration strength
    \enddata
\end{deluxetable*}
\vspace{-24pt}

@@

The population-averaged nucleosynthetic yields of CCSNe are still fairly uncertain. This problem is exacerbated by the complexity of the CCSN explosion landscape \citep{sukhbold_core-collapse_2016}. Recently, \citet{weinberg_scale_2024} used a measurement of the mean Fe yield of CC SNe by \citet{rodriguez_iron_2023} and the observed \aFe plateau at low metallicity to infer population-averaged yields of $y/Z_\odot\approx1$ --- in other words, the scale of SN yields relative to the Solar abundance is of order unity.

@@

We increased $y_{\rm Fe}^{\rm Ia}$ by a factor of 30\% and 10\% for the {\tt yZ1} and {\tt yZ2} yield sets, respectively, to ensure our models could reach ${\rm [O/Fe]}\approx0.0$ by the end time. The final row of Table \ref{tab:yields} reports the integrated SN Ia rate $N_{\rm Ia}/M_\star$ from each yield set, assuming a mean Fe yield per SN Ia of $\overline m_{\rm Fe}^{\rm Ia}=0.7$ M$_\odot$ \citep{mazzali_common_2007,howell_effect_2009}. The rate for the {\tt yZ1} yield set is slightly higher than the volumetric rate of $N_{\rm Ia}/M_\star=(1.3\pm0.1)\times10^{-3}\,{\rm M}_\odot^{-1}$ reported by \citet{maoz_star_2017}, but is consistent with their measurement of $N_{\rm Ia}/M_\star=(1.6\pm0.3)\times10^{-3}\,{\rm M}_\odot^{-1}$ for field galaxies. The rate for the {\tt yZ2} yield set is consistent with the measurement of $N_{\rm Ia}/M_\star=(2.2\pm1.0)\times10^{-3}\,{\rm M}_\odot^{-1}$ by \citet{maoz_type-ia_2012}.

The SN Ia rate in units of ${\rm M}_\odot^{-1}\,{\rm yr}^{-1}$ is defined as
\begin{equation}
    R_{\rm Ia}(t) = 
    \begin{cases}
        \frac{N_{\rm Ia}}{M_\star}
        \frac{f_{\rm Ia}(t)}{\int_{t_D}^{t_{\rm max}} f_{\rm Ia}(t') dt'}, & t \ge t_D \\
        0 & t < t_D,
    \end{cases}
    \label{eq:dtd-function}
\end{equation}
where $t_D=40\,{\rm Myr}$ is the minimum SN Ia delay time, $t_{\rm max}=13.2\,{\rm Gyr}$ is the lifetime of the disk, $N_{\rm Ia}/M_\star$ is the total number of SNe Ia per ${\rm M}_\odot$ of stars formed, and $f_{\rm Ia}(t)$ is the un-normalized form of the DTD. Motivated by the results of \citet{dubay_galactic_2024}, we adopt a wide plateau DTD of the form
\begin{equation}
    \label{eq:plateau-dtd}
    f_{\rm Ia}(t) =
    \begin{cases}
        1, & t < 1\,{\rm Gyr} \\
        (t/1\,{\rm Gyr})^{-1.1}, & t \ge 1\,{\rm Gyr}.
    \end{cases}
\end{equation}
We discuss the implications of using a different DTD in Section \ref{sec:abundance-distributions}.

\todo{Compare these yields to previous studies.}

@@

Figure \ref{fig:yield-outflow} also indicates the mode of the APOGEE abundance distributions in 1 Gyr-wide age bins. As explained by \citet{johnson_milky_2024}, the mode is expected to be less sensitive to the effects of radial migration than other statistical measures. The data show that the evolution in [O/H] is close to flat over the past 5 Gyr. The behavior of the $y/Z_\odot=2$ and $y/Z_\odot=3$ models closely matches this trend in the data, whereas the $y/Z_\odot=1$ model shows significant evolution of $\sim0.2$ dex during the same time period. The [Fe/H] abundance in the data does increase slightly at late times, likely due to the delayed contribution of Fe from SNe Ia. Between lookback times of $\sim5-9\,{\rm Gyr}$, the modes of [O/H] and [Fe/H] are actually higher than the present-day, likely due to a larger population of migrated stars relative to stars born in-situ at those times. The [O/Fe] evolution of all three models is nearly identical over the past 5 Gyr, and shows a similar evolution to the data apart from a $\sim0.05$ dex offset. \todo{Is this offset a problem? I could raise the SN Ia yields, but the global distributions would not match quite as well.}

\begin{figure}
    \centering
    \includegraphics{figures/yield_outflow.pdf}
    \caption{The abundance evolution of three one-zone models with different yield and outflow settings. Table \ref{tab:yields} presents the population-averaged yields for each model. The gray points with error bars indicate the mode of the APOGEE abundance distributions from the Solar neighborhood ($7\leq R_{\rm gal}\leq 9\,{\rm kpc}$, $0\leq|z|\leq0.5\,{\rm kpc}$) in 1 Gyr-wide bins of the \citet{leung_variational_2023} age estimates.}
    \label{fig:yield-outflow}
\end{figure}

@@

Most of the previous two-infall studies assume no mass-loaded outflows. Even in studies such as \citet{palicio_analytic_2023} which do incorporate Galactic winds, they are relatively weak ($\eta\approx0.2$).

\todo{Motivate our use of outflows. Connect to James' equilibrium paper.}

\citet{weinberg_equilibrium_2017} showed that in the limit of continuous star formation, the ISM abundance approaches an equilibrium which is determined by the balance of yields, outflows, and star formation. We calculate the mass-loading factor required to reach equilibrium at the Solar abundance as
\begin{equation}
    \eta_\odot = y_{\rm O}^{\rm CC} / Z_{\rm O,\odot} - 1 + r + \tau_\star / \tau_{\rm SFH},
\end{equation}
where $r=0.4$ is the instantaneous recycling parameter, $\tau_\star$ is the star formation efficiency timescale, and $\tau_{\rm SFH}$ is the star formation timescale.

We adopt a fiducial prescription for the outflow mass-loading factor which increases exponentially with radius:
\begin{equation}
    \eta(R_{\rm gal}) = \eta_\odot \exp\Big(\frac{R_{\rm gal}-R_\odot}{R_\eta}\Big)
\end{equation}
where $R_\odot=8\,{\rm kpc}$. As discussed by \citet{johnson_milky_2024}, the exponential outflow scale radius $R_\eta$ sets the equilibrium abundance gradient $\nabla{\rm [O/H]}_{\rm eq}$:
\begin{equation}
    R_\eta = -\frac{1}{\nabla{\rm [O/H]}_{\rm eq} \times\ln(10)}.
\end{equation}
We adopt $R_\eta=7.2\,{\rm kpc}$ as our fiducial value, which corresponds to $\nabla{\rm [O/H]}_{\rm eq}=-0.06$ dex kpc$^{-1}$.
\todo{Motivate exponential scale radius.}

@@

@@

\subsection{Radial Migration}
\label{sec:migration-discussion}

>>>>

% user-defined commands
% \newcommand{\yes}{\textcolor{green}{\checkmark}\xspace}
% \newcommand{\meh}{\textcolor{black}{$\sim$}\xspace}
% \newcommand{\no}{\textcolor{red}{$\times$}\xspace}
\newcommand{\osuaffil}{Department of Astronomy, The Ohio State University, 140 W. 18th Ave, Columbus OH 43210, USA}
\newcommand{\ccappaffil}{Center for Cosmology and AstroParticle Physics, The Ohio State University, 191 W. Woodruff Ave., Columbus OH 43210, USA}
\newcommand{\aFe}{[$\alpha$/Fe]\xspace}
\newcommand{\mathXH}{{\rm [X/H]}}
\newcommand{\mathOH}{{\rm [O/H]}}
\newcommand{\mathFeH}{{\rm [Fe/H]}}
\newcommand{\mathOFe}{{\rm [O/Fe]}}
\newcommand{\mathaFe}{{\rm [$\alpha$/Fe]}}
\newcommand{\yZ}[1]{$y/Z_\odot=#1$}
\newcommand{\vice}{{\tt VICE}\xspace}
% \newcommand{\hydro}{{\tt h277}\xspace}
\newcommand{\todo}[1]{{\color{red}#1}}

@@

% Title
\title{The Two-Infall Model Across Space and Time for a Milky Way in Equilibrium}

% Author list
% \author[]{Amanda Ash}
\author[0000-0003-3781-0747]{Liam O.\ Dubay}
\affiliation{\osuaffil}
\affiliation{\ccappaffil}
\author[0000-0001-7258-1834]{Jennifer A.\ Johnson}
\affiliation{\osuaffil}
\affiliation{\ccappaffil}
\author[0000-0002-6534-8783]{James W.\ Johnson}
\affiliation{Observatories of the Carnegie Institution for Science, 813 Santa Barbara St., Pasadena CA 91101, USA}
% \affiliation{\osuaffil}
% \affiliation{\ccappaffil}
\author[0000-0002-2854-5796]{John D.\ Roberts}
\affiliation{\osuaffil}
\affiliation{\ccappaffil}
% \author[0000-0001-7775-7261]{David H. Weinberg}
\author{coauthors}

@@

\begin{abstract}
    The two-infall model has long been proposed to explain the formation of the Milky Way's thick and thin disks through two consecutive gas accretion episodes. It has successfully reproduced observed abundance patterns such as the [$\alpha$/Fe]-bimodality in the Solar neighborhood and across the disk. However, few studies have explored a two-infall model with significant mass-loaded outflows, nor compared model results with comprehensive age--abundance data across the disk. We run multi-zone galactic chemical evolution (GCE) models with a two-infall star formation history, radially-dependent mass-loaded outflows, and a prescription for radial migration of stellar populations. We compare our model results to abundance patterns across the disk from the Apache Point Observatory Galactic Evolution Experiment (APOGEE) data release 17, supplemented with stellar age estimates using multiple methods. We find that the two-infall model struggles to reproduce all the observed characteristics of the chemical thin disk. Models with low nucleosynthetic yields and weak outflows experience long-lasting dilution of the gas-phase metallicity which contradicts the local age--metallicity relation. Conversely, models with higher yields and stronger outflows fail to reproduce the thin disk [$\alpha$/Fe] distribution. These issues can be mitigated, but not completely solved, by pre-enriching the accreted gas to low metallicity. In the context of the equilibrium scenario recently proposed by \citet{johnson_milky_2024}, the two-infall model must overcome these inherent limitations to be compatible with all observations.
\end{abstract}

@@

% \todo{Hook, summary of alpha-bimodality.}
Studies of galactic chemical evolution (GCE) aim to explain observed stellar abundance patterns by modeling the star formation history of the Milky Way. A long-standing paradigm of GCE has been that the metallicity of the interstellar medium (ISM) increases over time due to supernova enrichment from successive generations of stars. In this view, one feature of the Milky Way disk that is difficult to explain is the so-called ``$\alpha$-bimodality'': the presence of two populations of stars at similar metallicity but separated by their \aFe ratio \citep[e.g.,][]{bensby_exploring_2014}. The high-$\alpha$ sequence consists of old stars \citep[$\sim9$ Gyr;][]{pinsonneault_apokasc-3_2025} with super-Solar \aFe and is associated with the kinematic thick disk \citep[e.g.,][]{fuhrmann_nearby_1998}, while the low-$\alpha$ sequence is younger, with approximately Solar \aFe, and is associated with the thin disk. The $\alpha$-bimodality is present across the Galactic disk, but the relative strength of the high- and low-$\alpha$ sequences varies by location \citep{hayden_chemical_2015}.

% Summary of two-infall literature
The two-infall model of chemical evolution was proposed by \citet{chiappini_chemical_1997} to explain the origin of the thick and thin disks. Though the model has been revised and refined since, the basic premise remains the same: the rate of gas infall onto the Galaxy is described by two consecutive, exponentially declining bursts. The relatively low infall rate between the two bursts leads to a hiatus in the star formation rate, allowing the gas abundance to evolve between the high- and low-$\alpha$ sequences without producing many stars in between. 
% By varying the timescale of the second infall, the model can produce inside-out disk growth and a radial abundance gradient.
The initial model of \citet{chiappini_chemical_1997} successfully reproduced the available abundance data at the time, which were largely confined to the Solar neighborhood.

Subsequent studies refined the two-infall model to reproduce abundance data across the disk \citep[e.g.,][]{chiappini_abundance_2001,chiappini_oxygen_2003}, and others have explored in its context the SN Ia delay-time distribution \citep{matteucci_effect_2009,palicio_analytic_2023}, galactic fountains \citep{spitoni_effects_2009}, radial gas flows \citep{spitoni_effects_2011,palla_chemical_2020}, a variable star formation efficiency \citep{spitoni_effects_2011,palla_chemical_2020}, radial stellar migration \citep{spitoni_effect_2015,palla_mgfe_2022}, azimuthal abundance variations due to spiral modes \citep{spitoni_2d_2019}, and pre-enriched gas infall \citep{palla_chemical_2020,spitoni_remind_2024}. Recently, \citet{spitoni_beyond_2023} and \citet{palla_mapping_2024} proposed a third gas accretion event in the last $\sim3$ Gyr to match the inferred star formation history from {\it Gaia} \citep{ruiz-lara_recurrent_2020} and explain the recent abundance evolution of the Solar neighborhood.

\todo{Observational evidence.} \citet{nissen_high-precision_2020} measured abundances and estimated ages for nearby Solar-type stars and reported two sequences in the age--metallicity distribution which could be explained by the two-infall model \todo{(rewrite)}. \citet{chen_recent_2025}

\todo{Outflows.} Most previous studies of the two-infall model do not include mass-loaded outflows. Some hydrodynamic simulations of Galactic fountains ejected by CC SNe have shown that ejected material falls back onto the disk on relatively short timescales \citep{spitoni_galactic_2008,spitoni_effects_2009} and close to the point of origin \citep{melioli_hydrodynamical_2008,melioli_hydrodynamical_2009}, suggesting the effect on GCE could be minimal. However, other simulations of MW-like galaxies with different feedback prescriptions do produce mass-loaded outflows \todo{(citations)}. Empirically, mass-loaded outflows have been observed in nearby starburst galaxies \todo{(citations)} and dwarf galaxies \todo{(citations)} but not MW-like systems due to current detection limits \todo{(citations)}. We adopt an {\it ad hoc} prescription for outflows as a function of radius in order to balance different yield sets and reproduce the radial metallicity gradient.

\todo{Migration.} The two-infall model attempts to reproduce the full distribution of stellar abundances in the Solar neighborhood through a single, continuous evolutionary track. \todo{Talk about migration studies and why we don't need a single evolutionary track to explain the bimodality.}

@@

\begin{table*}
    \centering
    \caption{Median and dispersion in APOGEE parameter uncertainties.}
    \label{tab:uncertainties}
    \begin{tabular}{lcc}
        \hline\hline
        \multicolumn{1}{c}{Parameter} & \multicolumn{1}{c}{Median Uncertainty} & \multicolumn{1}{c}{Uncertainty Dispersion ($95\%-5\%$)} \\
        \hline
        [Fe/H]          & $0.0089$   & $0.0060$ \\
        $\mathOFe$  & $0.019$    & $0.031$ \\
        $\log_{10}(\tau_{\rm latent}/{\rm Gyr})$    & 0.10   & $0.16$ \\
        $\tau_{\rm [C/N]}/{\rm Gyr}$     & 1.0   & \todo{N/A} \\
        \hline
    \end{tabular}
\end{table*}

@@

Our second age catalog uses the [C/N]--age relation for red giant branch and red clump stars. 
\todo{Paragraph describing [C/N]-derived ages (get help from Jack).}
This method has the benefit of providing age estimates for luminous giants, which increases the sample size at larger distances from the Sun. However, systematic effects of the [C/N]--age relation mean that these ages are most trustworthy in the range $1\sim10$ Gyr. We estimate ages for \num{113464} stars across the disk, including \num{20995} in the Solar neighborhood.
\todo{Note about metallicity cutoff for luminous giants.}

@@

\begin{deluxetable*}{Cccl}
    \tablecaption{A summary of variables and their fiducial values for our chemical evolution models (see discussion in Section \ref{sec:methods}).\label{tab:multizone-parameters}}
    \tablehead{
        \colhead{Quantity} & \colhead{Fiducial Value(s)} & \colhead{Section} & \colhead{Description}
    }
    \startdata
        % Yields
        % y/Z_\odot       & 1         & \ref{sec:yields}  & Nucleosynthetic yield scaling (see Table \ref{tab:yields}) \\
        % N_{\rm Ia}/M_\star  & $1.55\times10^{-3}$       & \ref{sec:yields}  & Integrated Type Ia supernova rate (see Table \ref{tab:yields}) \\
        f_{\rm Ia}(t)   & Equation \ref{eq:plateau-dtd}   & \ref{sec:yields}  & Delay-time distribution of Type Ia supernovae \\
        % t_D             & 40 Myr    & \ref{sec:yields}  & Minimum SN Ia delay time \\
        % Star formation histories
        % Outflows
        % \eta_\odot      & 0.2       & \ref{sec:outflows}    & Outflow mass-loading factor in the Solar annulus ($\eta\equiv \dot\Sigma_{\rm out}/\dot\Sigma_\star$) \\
        R_\eta          & 5.0 kpc   & \ref{sec:outflows}    & Exponential outflow scale radius \\
        f_{\Sigma,0}    & 0.27      & \ref{sec:sfh}     & Central thick/thin disk surface density ratio \\
        \mathXH_{\rm CGM}   & Pristine  & \ref{sec:sfh}     & Metallicity of infalling gas \\
        \tau_1          & 1 Gyr     & \ref{sec:parameter-selection}     & Timescale of the first infall epoch \\
        \tau_2(R_\odot)  & 15 Gyr    & \ref{sec:parameter-selection}     & Timescale of the second infall epoch at the Solar annulus \\
        R_{\tau_2}   & 7 kpc     & \ref{sec:parameter-selection}      & Exponential scale radius of the second infall timescale \\
        t_{\rm max}      & 4.2 Gyr  & \ref{sec:parameter-selection}     & Time of maximum gas infall (onset of second infall) \\
        \sigma_{\rm RM8}    & 2.68 kpc  & \ref{sec:migration}   & Radial migration strength
    \enddata
\end{deluxetable*}
\vspace{-24pt}

@@

@@

The population-averaged nucleosynthetic yields of CCSNe are still fairly uncertain. This problem is exacerbated by the complexity of the CCSN explosion landscape \citep{sukhbold_core-collapse_2016}. Recently, \citet{weinberg_scale_2024} used a measurement of the mean Fe yield of CC SNe by \citet{rodriguez_iron_2023} and the plateau in stellar \aFe abundances at low metallicity to infer population-averaged yields of $y/Z_\odot\approx1$ --- in other words, the scale of SN yields is similar to the Solar abundance. However, \citet{johnson_milky_2024} found that GCE models with yields at this scale approach present-day abundances too slowly. We therefore investigate yield sets at multiple scales, which are presented in Table \ref{tab:yields}.

The SN Ia yield of Fe, $y_{\rm Fe}^{\rm Ia}$, is calculated so that the combined Fe yield $y_{\rm Fe}^{\rm Ia+CC}=y/Z_\odot$. We further increase $y_{\rm Fe}^{\rm Ia}$ by a factor of 30\% and 10\% for the \yZ{1} and \yZ{2} yield sets, respectively, to ensure that our models reach $\mathOFe\approx0.0$ by the end time. The fifth row of Table \ref{tab:yields} reports the integrated SN Ia rate $N_{\rm Ia}/M_\star$ from each yield set, assuming a mean Fe yield per SN Ia of $\overline m_{\rm Fe}^{\rm Ia}=0.7$ M$_\odot$ \citep{mazzali_common_2007,howell_effect_2009}. The rate for the \yZ{1} yield set is slightly higher than the volumetric rate of $N_{\rm Ia}/M_\star=(1.3\pm0.1)\times10^{-3}\,{\rm M}_\odot^{-1}$ reported by \citet{maoz_star_2017}, but is consistent with their measurement of $N_{\rm Ia}/M_\star=(1.6\pm0.3)\times10^{-3}\,{\rm M}_\odot^{-1}$ for field galaxies. The rate for the \yZ{2} yield set is consistent with the measurement of $N_{\rm Ia}/M_\star=(2.2\pm1.0)\times10^{-3}\,{\rm M}_\odot^{-1}$ by \citet{maoz_type-ia_2012}, while the rate for the \yZ{3} yield set is generally higher than literature values.

Unlike CCSNe, SNe Ia populate a broad distribution of delay times between progenitor formation and explosion. The time-dependent SN Ia rate in units of ${\rm M}_\odot^{-1}\,{\rm yr}^{-1}$ is defined as
\begin{equation}
    R_{\rm Ia}(t) = 
    \begin{cases}
        \frac{N_{\rm Ia}}{M_\star}
        \frac{f_{\rm Ia}(t)}{\int_{t_D}^{t_{\rm max}} f_{\rm Ia}(t') dt'}, & t \ge t_D \\
        0 & t < t_D,
    \end{cases}
    \label{eq:dtd-function}
\end{equation}
where $t_D=40\,{\rm Myr}$ is the minimum SN Ia delay time, $t_{\rm max}=13.2\,{\rm Gyr}$ is the lifetime of the disk, $N_{\rm Ia}/M_\star$ is the total number of SNe Ia per unit mass of star formation, and $f_{\rm Ia}(t)$ is the un-normalized form of the DTD. Motivated by the finding by \citet{dubay_galactic_2024} that a large fraction of long-delayed SNe Ia improves agreement with the Milky Way's high-$\alpha$ sequence, we adopt a wide plateau DTD of the form
\begin{equation}
    \label{eq:plateau-dtd}
    f_{\rm Ia}(t) =
    \begin{cases}
        1, & t < 1\,{\rm Gyr} \\
        (t/1\,{\rm Gyr})^{-1.1}, & t \ge 1\,{\rm Gyr}.
    \end{cases}
\end{equation}
We discuss the implications of using a different DTD in Section \ref{sec:abundance-distributions}.

\todo{I'd like to compare these yields to previous studies, but it's been very difficult to make that comparison. I'm unsure whether the \citet{francois_evolution_2004} yields are net or gross (probably gross since their baseline is \citet{woosley_evolution_1995}). I tried to implement their yield tables in VICE, but the chemical evolution tracks came out looking very wrong. Also, they use a weird IMF.} \citet{francois_evolution_2004} report that their models are insensitive to changes in the yield at a factor of 2 level.

@@

Figure \ref{fig:yield-outflow} also indicates the mode of the APOGEE abundance distributions in 1 Gyr-wide age bins. As explained by \citet{johnson_milky_2024}, the mode is expected to be less sensitive to the effects of radial migration than other statistical measures. The data show that the evolution in [O/H] is close to flat over the past 5 Gyr. The behavior of the $y/Z_\odot=2$ and $y/Z_\odot=3$ models closely matches this trend in the data, whereas the $y/Z_\odot=1$ model increases significantly by $\sim0.2$ dex during the same time period. The [Fe/H] abundance in the data does increase slightly at late times, likely due to the delayed contribution of Fe from SNe Ia. Between lookback times of $\sim5-9\,{\rm Gyr}$, the modes of [O/H] and [Fe/H] are higher than the present-day, likely due to a larger population of migrated stars relative to stars born in-situ at those times.

The three models in Figure \ref{fig:yield-outflow} predict nearly identical evolution in [O/Fe] over the past 5 Gyr, and the trend in the data is similar apart from a $\sim0.05$ dex offset. \todo{Is this offset a problem? I could raise the SN Ia yields, but the global distributions would not match quite as well.} The offset between the data and models grows between $\sim5-8\,{\rm Gyr}$, especially for the higher yields. Of the three, the \yZ{2} and \yZ{3} models most closely match the observed late-time age--metallicity relations, whereas the \yZ{1} model shows the best agreement with the observed [O/Fe] evolution. As the $y/Z_\odot=2$ and $y/Z_\odot=3$ models show generally similar behavior, we focus on the $y/Z_\odot=1$ and $y/Z_\odot=2$ yield sets for this work.

\begin{figure}
    \centering
    \includegraphics{figures/yield_outflow.pdf}
    \caption{The abundance evolution of three one-zone models with different yield and outflow settings. Table \ref{tab:yields} presents the population-averaged yields for each model. The gray points with error bars indicate the mode of the APOGEE abundance distributions from the Solar neighborhood ($7\leq R_{\rm gal}<9\,{\rm kpc}$, $0\leq|z|<0.5\,{\rm kpc}$) in 1 Gyr-wide bins of the \citet{leung_variational_2023} age estimates.}
    \label{fig:yield-outflow}
\end{figure}

@@

Most studies of the two-infall model assume the Milky Way has no significant mass-loaded outflows. Even in studies which do incorporate Galactic winds, the mass-loading is relatively weak \citep[e.g., $\eta\approx0.2$ in][]{palicio_analytic_2023}. To achieve a realistic radial metallicity gradient, many studies use a prescription for the infall timescale of the thin disk which increases linearly with radius \citep[e.g.,][]{chiappini_chemical_1997,romano_mass_2000}. Because we aim to study the effect of the yield assumptions on two-infall model predictions, we use mass-loaded outflows to control the final state of chemical evolution across the disk. As discussed by \citet{johnson_milky_2024}, evidence for or against outflows in Milky Way-type galaxies in simulations and observations is inconclusive.

\citet{weinberg_equilibrium_2017} showed that in the limit of continuous star formation, the ISM abundance approaches an equilibrium which is determined by the balance of yields, outflows, and star formation timescales. The mass-loading factor $\eta\equiv \dot\Sigma_{\rm out}/\dot\Sigma_\star$ required to reach equilibrium at Solar metallicity is
\begin{equation}
    \label{eq:equilibrium-eta}
    \eta_\odot = y_{\rm O}^{\rm CC} / Z_{\rm O,\odot} - 1 + r + \tau_\star / \tau_{\rm SFH},
\end{equation}
where $r=0.4$ is the instantaneous recycling parameter, $\tau_\star$ is the star formation efficiency timescale, and $\tau_{\rm SFH}$ is the star formation timescale. Equation \ref{eq:equilibrium-eta} informs our choice of $\eta$, but it is inaccurate in the two-infall case because of the bursty star formation history. Therefore, we tune the value of $\eta_\odot$ so that the model reaches $\mathOH=0.0$ by the end for each yield set, shown in Table \ref{tab:yields}.
% we find that if we adopt this prescription, models with $y/Z_\odot=1$ predict sub-Solar abundances at the present day because they have not yet reached their equilibrium value.

We adopt a prescription for the outflow mass-loading factor which increases exponentially with radius:
\begin{equation}
    \eta(R_{\rm gal}) = \eta_\odot \exp\Big(\frac{R_{\rm gal}-R_\odot}{R_\eta}\Big)
\end{equation}
where $R_\odot=8\,{\rm kpc}$. As discussed by \citet{johnson_milky_2024}, the exponential outflow scale radius $R_\eta$ sets the equilibrium abundance gradient $\nabla\mathOH_{\rm eq}$:
\begin{equation}
    R_\eta = -\frac{1}{\nabla\mathOH_{\rm eq} \times\ln(10)}.
\end{equation}
We adopt $R_\eta=7.2\,{\rm kpc}$ as our fiducial value, which corresponds to $\nabla\mathOH_{\rm eq}=-0.06$ dex kpc$^{-1}$.
\todo{Motivate exponential scale radius.}

@@

We note an important distinction between our method and that of \citet{spitoni_effect_2015}: SNe Ia from long-lived progenitors contribute Fe to each zone they migrate through, not just their birth zone. This is important because the median delay time of our SN Ia DTD is $\sim2$ Gyr, for which the width of the migration distribution is $\sigma_{\rm RM}\approx2$ kpc (Equation \ref{eq:radial-migration}). So, a significant fraction of SN Ia progenitors born in a given zone will enrich a disparate region of the Galaxy.

@@
